\subsection{Suicidator City Generator:} % (fold)
\label{sub:suicidator_city_generator}


http://cgchan.com/suicidator/index.php
Suicidator is an addon for the 3d application Blender.


“It varies the colors, materials and procedural elements enough to produce a reasonable approximation of a city at a distance, but realism is not a goal, and it does not operate on real data at all.” (http://vterrain.org/Culture/BldCity/Proc/ )

% subsection suicidator_city_generator_ (end)

\subsection{ghostTown:} % (fold)
\label{sub:ghosttown}

http://kilad.net/site/
http://www.kilad.net/GTForum/


It’s a script plugin for 3DS Max from Autodesk.
“Ghost Town is a script that procedurally generates cities and urban environments in only a few clicks, and features a number of options. Such as low or high poly buildings, road layouts, vehicles, trees, facades and an easy to use material and texture system.” (http://cgi.tutsplus.com/tutorials/create-a-detailed-city-with-3d-studio-max-ghost-town--cg-10090)

% subsection ghosttown_ (end)

\subsection{Skyscraper:} % (fold)
\label{sub:skyscraper}

http://www.skyscrapersim.com/index.shtml
Standalone


“Skyscraper aims to be a fully-featured, modular, 3D realtime building simulator, powered by the Scalable Building Simulator (SBS) engine. The main feature SBS provides is a very elaborate and realistic elevator simulator, but also simulates general building features such as walls, floors, stairs, shaftwork and more. Many more things are planned, including gaming support (single and network multiplayer), and a graphical building designer. Skyscraper is written in C++ and uses the OGRE graphics engine, Bullet for collisions and physics, FMOD for sound, the wxWidgets GUI library, and is multiplatform. The current versions aim for a future 2.0 release.” from the official site.

% subsection skyscraper (end)

\subsection{Blended Cities:} % (fold)
\label{sub:blended_cities}

http://jerome.le.chat.free.fr/index.php/en/city-engine/
Addon for Blender

“Blended Cities is an open-source city generator for Blender. it allows to create quickly a large amount of streets and buildings, with various shapes. B.C. fights against squared things : curved streets and odd or cylindric buildings can be created simply, so you can create old towns, not only modern cities.”

% subsection blended_cities_ (end)