%!TEX root = ../report.tex

% 
% Overview
% 

\section{Overview} % (fold)
\label{sec:overview}


This Section will provide an overview over this topic providing background (\dots). The Section~\ref{sec:objectives} will address the objectives for this thesis work. Section~\ref{sec:related_work} will explore different related works to this program. Section~\ref{sec:architecture} will describe the architecture of the proposed solution. Section~\ref{sec:evaluation} will explain how our results will be evaluated and we will conclude on Section~\ref{sec:conclusions}.

\subsection{Procedural Generation} % (fold)
\label{sub:procedural_generation}


\emph{Procedural Generation} is the algorithmic generation of content instead of the usual manual creation of content. This can be applied in almost all forms of content, but is mostly used in graphics creation and sound (music and synthetic speech).

The key property of procedural generation is that in describes the data entity, be it geometry, texture or effect, in terms of a sequence of generation instructions rather than as a static block of data \cite{Kelly}. This allows anyone with less resources to produce high detailed, and high quality content.

\input{sections/3-1-Procedural_Modelling_Techniques.tex}


\subsection{Architectural Styles} % (fold)
\label{sub:architectural_styles}

Most buildings or other man made structures are classified by it's \emph{Architectural Style}. An architectural style is characterized by the features that make a building notable and historically identifiable. This style characterisics are related to form, building materials, construction methods, etc. and change trough different places and over the years. 

Even with this constant change in the styles there are some rules that we have to followed. The most obvious one is the chronological time.
If we are modelling a city from the 16th century it's wrong if we add buildings with styles form the 19th century. And we have to think also in a simmilar way with the places, if it's an asian city we do not add buildings with a known european layout.

And this correctness in relation to the architectural styles is also an important concern to this work.

% subsection architectural_styles (end)

% subsection procedural_generation (end)

% section overview (end)